%-------------------------
% Resume in LaTeX
% Based on sb2nov/jakegutierrez template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Niraj Ojha} \\ \vspace{2pt}
    \small 337-292-3058 $|$ \href{mailto:nischalojha2@gmail.com}{\underline{nischalojha2@gmail.com}} $|$ 
    \href{https://linkedin.com/in/NischalOjha}{\underline{linkedin.com/in/NischalOjha}} $|$
    \href{https://github.com/NirajO}{\underline{github.com/NirajO}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McNeese State University}{Lake Charles, LA}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- Dec. 2025}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Programmer}{Aug. 2022 -- Present}
      {McNeese State University}{Lake Charles, LA}
      \resumeItemListStart
        \resumeItem{Contributed to the development and maintenance of academic software used for instruction and research.}
        \resumeItem{Assisted in testing and debugging scripts utilized in classroom instruction and lab exercises.}
      \resumeItemListEnd

    \resumeSubheading
      {Tutor: Math \& Science}{2018 -- Present}
      {Freelance}{}
      \resumeItemListStart
        \resumeItem{Tutored students from middle school through college in mathematics and science to improve understanding and performance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Tetris Game} $|$ \emph{Java}}{Aug. 2023 -- Dec. 2023}
      \resumeItemListStart
        \resumeItem{Built a functional Tetris clone applying object-oriented design principles.}
        \resumeItem{Implemented real-time collision detection, piece rotation logic, and a scoring system.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Kiosk-based Food Ordering System} $|$ \emph{JavaScript, React, Node.js, HTML/CSS}}{Jan. 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Developed a responsive self-service kiosk interface for restaurants with organized menu categories.}
        \resumeItem{Implemented cart, payment flow, and receipt generation (frontend-first architecture).}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Tool Sharing Website} $|$ \emph{HTML, CSS, JavaScript}}{Jan. 2025 -- May 2025}
      \resumeItemListStart
        \resumeItem{Collaborated to create a web application for listing and renting tools with category-based browsing.}
        \resumeItem{Added user authentication and form handling for item posting and requests.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Banana Token} $|$ \emph{Solidity, Hardhat, React}}{2025}
      \resumeItemListStart
        \resumeItem{Created a mintable, ownable ERC-20 token; deployed and tested on the Sepolia testnet.}
        \resumeItem{Built a React frontend with MetaMask integration for mint, burn, transaction history, and dynamic symbol display.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP & TEAMWORK-----------
\section{Leadership \& Teamwork}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Captain, Local Cricket Team}{2016 -- 2019}
      {Damak, Jhapa, Nepal}{}
      \resumeItemListStart
        \resumeItem{Led a 15-member local cricket team in inter-school and community tournaments, fostering coordination and sportsmanship.}
        \resumeItem{Organized practice schedules, set match strategies, and motivated teammates to perform under pressure.}
      \resumeItemListEnd

    \resumeSubheading
      {Team Lead, School Project Collaboration}{2018 -- 2019}
      {Damak, Jhapa, Nepal}{}
      \resumeItemListStart
        \resumeItem{Guided a 4-member team on a science project; delegated tasks, set milestones, and ensured on-time delivery.}
        \resumeItem{Facilitated problem-solving discussions and final presentation quality, resulting in successful project outcomes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, PHP, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, PySide}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
